Introduction

### 2025-05-02 index.qmd
Update index.qmd with acknowledgements
small changes

---
title: "Selection of Variables and Functional Forms in Multivariable Analysis"
---

@@

Derive guidance for variable and function selection  in multivariable analysis.

@@

The main focus of TG2 is to identify influential variables and gain insight into their individual and joint relationship with the outcome. Two of the (interrelated) main challenges are selection of variables for inclusion in a multivariable explanatory model, and choice of the functional forms for continuous variables

@@

>>>>

---
title: "Introduction"
---

@@

The main aim of STRATOS topic group 2 is to develop guidance for variable and functional form selection in multivariable analyses.

@@

Multivariable models play a dominanting role in all kinds of empirical research, and they are used in addressing descriptive, predictive and explanatory research questions.

The main focus of multivariable model building is to identify influential variables and to gain insight into their individual and joint relationship with an outcome variable. Two of the (interrelated) main challenges are selection of variables for inclusion in a multivariable model, and choice of the functional forms for continuous variables.

On this website we list our activities, TG2 publications, further reading and resources, and the members of our topic group.

@@

### Acknowledgements

Many thanks to Marianne Huebner, who designed the website of the STRATOS Topic Group 3, which the website of Topic Group 2 is based on.
